% Data Science CV - Dhruv Varshney
% Compile: pdflatex data_cv.tex
\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0em}{}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}
\begin{center}
  {\LARGE \textbf{Dhruv Varshney} \hfill 23EX10013}\\
  \vspace{0.5em}
  \small Bachelor of Science in Exploration Geophysics (4-Year) --- Minor: Computer Science and Engineering\\
  \small Indian Institute of Technology, Kharagpur\\
  \vspace{0.5em}
  \normalsize \href{mailto:dhruvvarshney2906@gmail.com}{dhruvvarshney2906@gmail.com} $\mid$ +91 85979 86847
\end{center}

\section*{Education}
\begin{tabular}{@{}p{1.2cm} p{6.5cm} p{4.0cm} p{2.0cm}@{}}
\textbf{Year} & \textbf{Degree / Exam} & \textbf{Institution} & \textbf{CGPA / Marks} \\
2027 & 4 Year B.S & IIT Kharagpur & 8.3/10\\
2023 & Central Board of Secondary Education (CBSE) & Kendriya Vidyalaya IIT Kharagpur & 91.2\\
2021 & Central Board of Secondary Education (CBSE) & Kendriya Vidyalaya IIT Kharagpur & 97.6\\
\end{tabular}
\vspace{0.5em}
\small{* CGPA till 5th Semester}

\section*{Interests}
\begin{itemize}[left=0pt]
  \item \textbf{Applied Machine Learning:} LLMs, speech recognition, representation learning.
  \item \textbf{Data Engineering:} Scalable ETL, data quality automation, analytics infrastructure.
  \item \textbf{Statistical Modeling:} Experiment design and probabilistic analysis.
  \item \textbf{Information Retrieval:} Semantic search and knowledge graph enrichment.
  \item \textbf{Storytelling with Data:} Dashboarding and insight communication.
\end{itemize}

\section*{Experience}
\textbf{Analyst Programmer}, Xceedance Consulting Private Limited \hfill May '25 -- Oct '25\\
Extraction of information from insurance data using LLM workflows and domain-specific normalization.
\begin{itemize}
  \item Generated synthetic datasets with generative AI to cover edge-case policy structures.
  \item Performed exploratory data analysis and cleaning to improve downstream reliability.
  \item Normalized entity names and attributes for a consistent claims knowledge base.
  \item Built and evaluated a few-shot model on Azure AI API to classify insurance entities.
\end{itemize}

\vspace{0.5em}
\textbf{Vedvani --- Transcribing Spoken Sanskrit Shlokas} (Under Prof. Pawan Goyal) \hfill May '24 -- Nov '24\\
Engineered a speech-to-text pipeline and fine-tuned a Wav2Vec2 model for low-resource Sanskrit.
\begin{itemize}
  \item Scraped and aligned transcripts with audio recordings; normalized text preserving svaras.
  \item Fine-tuned transformer-based speech models and applied data augmentation for robustness.
  \item Evaluated using WER and CER with consistent gains.
\end{itemize}

\section*{Projects}
\textbf{Real-Time AI Emergency Evacuation System} --- Self Project\\
Engineered a computer vision system to compute optimal evacuation routes from live video.
\begin{itemize}
  \item Integrated YOLO for human detection and used homography to map detections to floorplans.
  \item Implemented A* pathfinding to regenerate safe routes under 50 ms.
  \item Optimized for 30 FPS using OpenCV and NumPy.
\end{itemize}

\vspace{0.5em}
\textbf{Prediction of House Prices} --- Kaggle\\
Developed regression models and feature engineering pipelines; achieved strong leaderboard placement.
\begin{itemize}
  \item Engineered 200+ features and compared multiple regression models including XGBoost.
  \item Used Bayesian optimization for hyperparameter tuning with cross-validation.
  \item Achieved high R$^2$ and competitive RMSE; Kaggle rank: 2,111.
\end{itemize}

\vspace{0.5em}
\textbf{Spaceship Titanic, Titanic Survival Prediction} --- Kaggle\\
Built end-to-end classification pipelines with careful feature engineering, tuning and evaluation.

\section*{Awards and Achievements}
\begin{itemize}
  \item Top 6.4\% in JEE Advanced 2023; top 1.9\% in JEE Mains 2023.
  \item Top 1\% in WBJEE among 100k+ candidates.
  \item Peak Codeforces rating 1400+ (Specialist); solved 150+ LeetCode problems.
  \item 4th place, Open IIT Data Analytics Competition 2024.
\end{itemize}

\section*{Skills}
\begin{itemize}
  \item \textbf{Languages:} Python, SQL, C++, Bash
  \item \textbf{ML \\& AI:} scikit-learn, TensorFlow, Hugging Face Transformers, OpenCV, spaCy
  \item \textbf{Data Ops:} Feature engineering, data validation, experiment tracking
  \item \textbf{Visualization:} Matplotlib, Seaborn, Plotly
\end{itemize}

\section*{Coursework}
Programming and Data Structures; Linear Algebra; Advanced Calculus; PDE; Probability and Statistics; Transform Calculus.

\section*{Positions of Responsibility}
Head of Design and Content Writing, Click Kgp --- photography and content design lead.

\vfill
\begin{center}\small{\copyright{} Dhruv Varshney | IIT Kharagpur | 2027}\end{center}
\end{document}
